Predicting the 2024 US Presidential Election with a Model-Based Forecast

### 2024-11-03 paper/paper.qmd
update abstract and introduction

---
title: "Predicting the 2024 US Presidential Election with a Model-Based Forecast"
subtitle: "Using Generalized Linear Models to Predict Election Outcomes"
author: 
  - Yuanyi (Leo) Liu
  - Dezhen Chen
  - Ziyuan Shen
thanks: "Code and data are available at: [Forecasting the 2024 US Presidential Election](https://github.com/leoyliu/Forecasting-the-2024-US-Presidential-Election)."
date: today
date-format: long
abstract: "In this paper, we develop a linear model to predict the outcome of the 2024 U.S. presidential election using a \"poll-of-polls\" approach that combines data from various prominent pollsters. Our analysis indicates that Donald Trump’s probability of winning varies between 45% and 55% across states, depending on regional polling trends. However, Kamala Harris is projected to secure key states and achieve a majority of electoral votes, with a projected count of 239 to Trump’s 98 based on the testing dataset. These predictions are based on the testing dataset, which lacks data for some states, limiting our ability to produce results for all states. This paper underscore the effectiveness of aggregated polls in producing reliable election forecasts."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Our findings suggest that while Trump has a competitive chance, Harris is projected to win key states and receive a majority of electoral votes. Harris will receive 239 electoral votes to Trump's 98 votes. This is important because accurate election forecasts help reduce uncertainty, which allows political stakeholders to allocate resources efficiently and gives the public a better understanding of likely outcomes. Aggregate polling reduces uncertainty and provides a clearer picture of potential outcomes.

@@

## Estimand

In this study, our estimand is Donald Trump's percentage of polling in each state ahead of the 2024 U.S. presidential election. The object of the estimation is Trump's percentage of polling data in each state based on aggregated information from various sources By using a linear regression model, we aim to capture changes in public opinion over time and provide a clearer understanding of voter preferences and the likely election outcome.

>>>>

---
title: "Predicting the 2024 US Presidential Election with a Model-Based Forecast"
subtitle: "Using Generalized Linear Models to Predict Election Outcomes"
author: 
  - Yuanyi (Leo) Liu
  - Dezhen Chen
  - Ziyuan Shen
thanks: "Code and data are available at: [Forecasting the 2024 US Presidential Election](https://github.com/leoyliu/Forecasting-the-2024-US-Presidential-Election)."
date: today
date-format: long
abstract: "In this paper, we develop a linear model to predict the outcome of the 2024 U.S. presidential election using a \"poll-of-polls\" approach that aggregates data from multiple well-known pollsters. Our analysis projects that Donald Trump's probability of winning ranges from 30% to 52%, which depends on regional polling trends. However, Kamala Harris is projected to secure key states and obtain the majority of electoral votes, with a predicted count of 341 to Trump's 197 based on the testing dataset. These predictions are based on the testing dataset, which lacks data for some states, limiting our ability to produce results for all states. This paper underscores the effectiveness of aggregated polls in producing reliable election forecasts."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

In this study, our estimand is Donald Trump's percentage of polling in each state ahead of the 2024 U.S. presidential election. The object of the estimation is Trump's percentage of polling data in each state based on aggregated information from various sources. By using a linear regression model, we aim to capture changes in public opinion over time and provide a clearer understanding of voter preferences and the likely election outcome.

Our findings suggest that while Trump has a competitive chance, Harris is projected to win key states and receive a majority of electoral votes. Harris is estimated to receive 341 electoral votes to Trump's 197, and the uncertainty around these estimates is represented by confidence intervals, which take into account polling changes and model assumptions. This is important because accurate election forecasts help reduce uncertainty, which allows political stakeholders to allocate resources efficiently and gives the public a better understanding of likely outcomes. Aggregate polling reduces uncertainty and provides a clearer picture of potential outcomes.

@@
